Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-14 hscc2017/paper.tex
hscc17

Using an optimization tool, the authors
of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
controller for this plant, which is characterized by the following
$z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the
closed-loop system for the discrete plant model $G(z)$ in~\eqref{Eq:running-example-plant}.  
However, if the effects of finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
FWL), then this closed-loop system becomes unstable.
%
For instance, an implementation of $C(z)$ using 
$\mathbb R \param {4}{16}$ fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as: 
\red{[wait I'm confused: the next should be a tilde!!]}
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{.47\textwidth}{!}{
$\hat{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
}
\end{equation} 
%
The resulting system using the typical series loop configuration, where
$\hat{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
\red{[hang in there - did we not consider FWL on $G(z)$? why not?]}
Figure~\ref{fig:original} gives the Bode diagram for the digital controller
represented in~\eqref{Eq:running-example-controller}: 
as the phase margin is negative, 
the controller is unstable when considering the above FWL effects.

\subsection{Program Synthesis for the Example}
%
We now demonstrate how our approach solves the synthesis problem for the
example given in the previous section.  
Assuming a precision of $I_p=16$, $F_p=24$,  
\blue{[so you mean we're not using Jury's criterion? pllease clarify.] the digital controller is designed with standard techniques for
control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}. 
}
We start with an a-priori candidate solution with all coefficients zero: 
%
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
%
%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$ 
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
$$

In the first {\sc verify} stage, the {\sc uncertainty} 
check finds the following counterexample:
%
$$ 
\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}. 
$$
%$$
%\begin{array}{ll}
%\Delta N_G(z) = 0.026506\\
%\Delta D_G(z) = 1.000610z+1.002838
%\end{array}
%$$ 
We add this counterexample to {\sc inputs} and initiate the {\sc synthesize}
phase, where we obtain the following candidate solution:
%
%\red{[ How is the order of the candidate solution chosen here?]}
$$
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}. 
$$ 
This time, the {\sc uncertainty} check does not find any
counterexample and we pass the current candidate solution to the {\sc
precision} verification stage.
%
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
%
We obtain the result $\mathit{false}$, meaning that the current precision is
insufficient.  Consequently, we increase our precision to $I_p=20$, $F_p=28$.
%
Since the previous counterexamples were obtained at lower precision, we
remove them from the set of counterexamples.  Back in the {\sc synthesize}
phase, we re-start the process with a candidate solution with all
coefficients $0$, as above.  Next, the {\sc uncertainty} verification stage provides
the first counterexample at higher precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$ 
\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}. 
$$
In the {\sc synthesize} phase, we get a new candidate solution that
eliminates the new, higher precision counterexample:
%
$$ 
C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}. 
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

>>>>

Using an optimization tool, the authors
of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
controller for this plant, which is characterized by the following
$z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the
closed-loop system for the discrete plant model $G(z)$ in~\eqref{Eq:running-example-plant}.  
However, if the effects of finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
FWL), then this closed-loop system becomes unstable.
%
For instance, an implementation of $C(z)$ using 
$\mathbb R \param {4}{16}$ fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as: 
\red{[wait I'm confused: to be precise, the next should be a tilde in view of the preceding comments on FWL!!] notice we are indeed approximating a C, so the equality comments from above do not apply! correct?}
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{.47\textwidth}{!}{
$\hat{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
}
\end{equation} 
%
The resulting system using the typical series loop configuration, where
$\hat{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
\red{[hang in there - did we not consider FWL on $G(z)$? why not?]}
Figure~\ref{fig:original} gives the Bode diagram for the digital controller
represented in~\eqref{Eq:running-example-controller}: 
as the phase margin is negative, 
the controller is unstable when considering the above FWL effects.

\subsection{Program Synthesis for the Example}
%
We now demonstrate how our approach solves the synthesis problem for the
example given in the previous section.  
Assuming a precision of $I_p=16$, $F_p=24$,  
\blue{[so you mean we're not using Jury's criterion? pllease clarify.] the digital controller is designed with standard techniques for
control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}. 
}
We start with an a-priori candidate solution with all coefficients zero: 
%
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
%
%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$ 
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
$$
\blue{[here recall that indeed this C equates to the tilde version, because \ldots ]}
In the first {\sc verify} stage, the {\sc uncertainty} 
check finds the following counterexample:
%
$$ 
\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}. 
$$
%$$
%\begin{array}{ll}
%\Delta N_G(z) = 0.026506\\
%\Delta D_G(z) = 1.000610z+1.002838
%\end{array}
%$$ 
We add this counterexample to {\sc inputs} and initiate the {\sc synthesize}
phase, where we obtain the following candidate solution:
%
%\red{[ How is the order of the candidate solution chosen here?]}
$$
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}. 
$$ 
This time, the {\sc uncertainty} check does not find any
counterexample and we pass the current candidate solution to the {\sc
precision} verification stage.
%
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
%
We obtain the result $\mathit{false}$, meaning that the current precision is
insufficient.  Consequently, we increase our precision to $I_p=20$, $F_p=28$.
%
Since the previous counterexamples were obtained at lower precision, we
remove them from the set of counterexamples.  Back in the {\sc synthesize}
phase, we re-start the process with a candidate solution with all
coefficients $0$, as above.  Next, the {\sc uncertainty} verification stage provides
the first counterexample at higher precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$ 
\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}. 
$$
In the {\sc synthesize} phase, we get a new candidate solution that
eliminates the new, higher precision counterexample:
%
$$ 
C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}. 
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$
